Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-01-27 manuscript/draft_rsfmri.Rmd

## Interaction effect group by time on aggregated FC (preregistered analysis)
```{r load agg FC data and prepare, echo=FALSE}
agg_FC_DMN=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/DMN/agg_FC_DMN.txt")
agg_FC_DMN_ID=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/DMN/agg_FC_DMN_ID.txt")
agg_FC_Rew_ID=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/Rew/agg_FC_Rew_ID.txt")
agg_FC_Rew=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/Rew/agg_FC_Rew.txt")
for (i in c(1:nrow(agg_FC_DMN_ID))){
  agg_FC_Rew[i,"subj.ID_tp"]=strsplit(base::strsplit(as.character(agg_FC_Rew_ID[i,"V1"]),'/')[[1]][10],'_nacc')[[1]][1]
  agg_FC_DMN[i,"subj.ID_tp"]=strsplit(base::strsplit(as.character(agg_FC_DMN_ID[i,"V1"]),'/')[[1]][10],'_pcc')[[1]][1]
}

@@

```{r DMN2tp results age, sex, caption="DMN connectivity compared bl to fu, adjusted for age and sex", results="asis", eval=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), custom.model.names = c("R0", "R1"), float.pos = "h",  custom.coef.names=c("Intercept (BL, NBARS)", "Timepoint FU", "Group BARS", "Age", "Sex", "Timepoint x Group"),  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```

@@

p_mean_BMI=anvmeanBMI$`Pr(>Chisq)`
```
The association also remained significant when we split mFD into average and change in mFD (p = `r round(p_mean_BMI,4)`) and there was no significant association of mean or change in mFD with DMN FC.

@@

test_vif=lm(mean_Rew_conn ~ mean.BMI + within.BMI + mean.logmFD + within.logmFD +  Age_BL + Sex, data=final_FC)
vif_res=vif(test_vif)
``` 
As expected from the whole-brain findings, there was no association of mean BMI or within-subject BMI change and reward network connectivity in models adjusting for age, sex and mFD.

@@

### Effect of FD (exploratory analysis)
#### Whole-brain analysis
To investigate the unique contributions of the average value of and the longitudinal change in mFD, we constructed two additional models. 
First, BMI measures are excluded from the design matrix. Covariance of the mFD and outcome measures is investigated by splitting mFD into average mFD and longitudinal mFD change and by inspecting associations with each predictor. Age and sex were nuisance covariates.
<!-- #### Reward -->
As shown in Table \@ref(tab:tableFDmodel), there was a significant association between mFD and co-activation of NAcc with one cluster located in proximity to the central sulcus and motor areas . Cluster co-activation appeared irrespective of the preprocessing procedure, differing mainly in cluster size.
<!-- ### DMN -->
We did not find a any clusters for functional connectivity with the PCC.
```{r "FDagesexNACCccavgFDact", fig.show = "hold", out.width = "50%", fig.cap="Positive association of mean mFD and FC of NAcc with cluster, adjusted for age, sex, mean BMI, change BMI and change mFD", fig.subcap=c("in AROMA+CC", "in AROMA+CC+GSR data")}
knitr::include_graphics("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/FDagesex_NACCcc_avgFD_act.pdf")
knitr::include_graphics("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/FDagesex_NACCgsr_avgFD_act.pdf")
```

<!-- Neurovault -->
Unthresholded maps for the t-tests as well as contrasts of average BMI and change BMI of the main model, and post-hoc contrasts for average FD and change FD will be are published on NeuroVault.

>>>>

## Interaction effect group by time on aggregated FC (preregistered analysis)
There was no significant time by group interaction for aggregated DMN and reward network FC (see Figures \@ref(fig:figaggDMN) and \@ref(fig:figaggRew) and supplements for a detailed summary of the models) 
```{r load agg FC data and prepare, echo=FALSE}
agg_FC_DMN=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/DMN/agg_FC_DMN.txt")
agg_FC_DMN_ID=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/DMN/agg_FC_DMN_ID.txt")
agg_FC_Rew_ID=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/Rew/agg_FC_Rew_ID.txt")
agg_FC_Rew=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/Rew/agg_FC_Rew.txt")
for (i in c(1:nrow(agg_FC_DMN_ID))){
  agg_FC_Rew[i,"subj.ID_tp"]=strsplit(base::strsplit(as.character(agg_FC_Rew_ID[i,"V1"]),'/')[[1]][10],'_nacc')[[1]][1]
  agg_FC_DMN[i,"subj.ID_tp"]=strsplit(base::strsplit(as.character(agg_FC_DMN_ID[i,"V1"]),'/')[[1]][10],'_pcc')[[1]][1]
}

@@

```{r DMN2tp results age, sex, caption="DMN connectivity compared bl to fu, adjusted for age and sex", results="asis", eval=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), custom.model.names = c("R0", "R1"), float.pos = "h",  custom.coef.names=c("Intercept (BL, NBARS)", "Timepoint FU", "Group BARS", "Age", "Sex", "Timepoint x Group"),  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)

@@

p_mean_BMI=anvmeanBMI$`Pr(>Chisq)`
```

The association also remained significant when we split mFD into average and change in mFD (p = `r round(p_mean_BMI,4)`) and there was no significant association of mean or change in mFD with DMN FC.

@@

test_vif=lm(mean_Rew_conn ~ mean.BMI + within.BMI + mean.logmFD + within.logmFD +  Age_BL + Sex, data=final_FC)
vif_res=vif(test_vif)
```

As expected from the whole-brain findings, there was no association of mean BMI or within-subject BMI change and reward network connectivity in models adjusting for age, sex and mFD.

@@

### Effect of FD (exploratory analysis)
#### Whole-brain analysis
To investigate the unique contributions of the average value of and the longitudinal change in mFD, we constructed two additional models. 
First, BMI measures are excluded from the design matrix. Covariance of the mFD and outcome measures is investigated by splitting mFD into average mFD and longitudinal mFD change and by inspecting associations with each predictor. Age and sex were nuisance covariates.

<!-- #### Reward -->
As shown in Table \@ref(tab:tableFDmodel), there was a significant association between mFD and co-activation of NAcc with one cluster located in proximity to the central sulcus and motor areas . Cluster co-activation appeared irrespective of the preprocessing procedure, differing mainly in cluster size.
<!-- ### DMN -->
We did not find a any clusters for functional connectivity with the PCC.
```{r "FDagesexNACCccavgFDact", fig.show = "hold", out.width = "50%", fig.cap="Positive association of mean mFD and FC of NAcc with cluster, adjusted for age, sex, mean BMI, change BMI and change mFD", fig.subcap=c("in AROMA+CC", "in AROMA+CC+GSR data")}
knitr::include_graphics("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/FDagesex_NACCcc_avgFD_act.pdf")
knitr::include_graphics("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/FDagesex_NACCgsr_avgFD_act.pdf")
```
